Stats for the convergence paper

### 2019-05-28 models/paper/convergence_paper_models.Rmd
fixing paths

setwd('~/Work/NZILBB/RaczBecknerHayPierrehumbert2019/models/paper')
```

@@

```{r }
source('~/Work/NZILBB/RaczBecknerHayPierrehumbert2019/functions/grabdata.R')

@@

save(fit1, file = '~/Work/NZILBB/RaczBecknerHayPierrehumbert2019/models/paper/bayes_fit1.rda')

@@

save(fit2, file = '~/Work/NZILBB/RaczBecknerHayPierrehumbert2019/models/paper/bayes_fit2.rda')

@@

save(fit3, file = '~/Work/NZILBB/RaczBecknerHayPierrehumbert2019/models/paper/bayes_fit3.rda')

@@

save(fit4, file = '~/Work/NZILBB/RaczBecknerHayPierrehumbert2019/models/paper/bayes_fit4.rda')

@@

loo.comparisons = loo_compare(fit1,fit2,fit3,fit4)
save(loo.comparisons, file = '~/Work/NZILBB/RaczBecknerHayPierrehumbert2019/models/paper/loo_comparisons.rda')

@@

load('~/Work/NZILBB/RaczBecknerHayPierrehumbert2019/models/paper/bayes_fit3.rda')
bayes_factor()

load('~/Work/NZILBB/RaczBecknerHayPierrehumbert2019/models/paper/loo_comparisons.rda')
loo.comparisons

@@

save(m3, file = '~/Work/NZILBB/RaczBecknerHayPierrehumbert2019/models/paper/m3.rda')

@@

save(m4, file = '~/Work/NZILBB/RaczBecknerHayPierrehumbert2019/models/paper/m4.rda')
```

@@

load('~/Work/NZILBB/RaczBecknerHayPierrehumbert2019/models/paper/m4.rda')
load('~/Work/NZILBB/RaczBecknerHayPierrehumbert2019/models/paper/m3.rda')

@@

m5 <- glmer(resp_post_reg ~ c.baseline_gcm_features + gcm_wf_score_diff + pre_reg_av + (1 + c.baseline_gcm_features + gcm_wf_score_diff | participant_id) + (1 | word), data = test2, family = binomial (link = logit), control=glmerControl(optimizer="bobyqa"))
save(m5, file = '~/Work/NZILBB/RaczBecknerHayPierrehumbert2019/models/paper/m5.rda')

m6 <- glmer(resp_post_reg ~ c.baseline_mgl_features + mgl_wf_score_diff + pre_reg_av + (1 + c.baseline_mgl_features + mgl_wf_score_diff | participant_id) + (1 | word), data = test2, family = binomial (link = logit), control=glmerControl(optimizer="bobyqa"))
save(m6, file = '~/Work/NZILBB/RaczBecknerHayPierrehumbert2019/models/paper/m6.rda')

@@

m7 <- glmer(resp_post_reg ~ c.individual_gcm_features + c.baseline_mgl_features + pre_reg_av + (1 + c.individual_gcm_features + c.baseline_mgl_features | participant_id) + (1 | word), data = test2, family = binomial (link = logit), control=glmerControl(optimizer="bobyqa"))
save(m7, file = '~/Work/NZILBB/RaczBecknerHayPierrehumbert2019/models/paper/m7.rda')

@@

```{r }
load('~/Work/NZILBB/RaczBecknerHayPierrehumbert2019/models/paper/m5.rda')
load('~/Work/NZILBB/RaczBecknerHayPierrehumbert2019/models/paper/m6.rda')
load('~/Work/NZILBB/RaczBecknerHayPierrehumbert2019/models/paper/m7.rda')

@@

t2 = test2 %>% 
  group_by(
    word, 
    lex_typicality
  ) %>% 
  summarise(
    post.reg.av = mean(resp_post_reg),
    individual_gcm_features = mean(individual_gcm_features),
    individual_mgl_features = mean(individual_mgl_features),
  ) %>% 
  ungroup() %>% 
  mutate(
    individual_gcm_features = scales::rescale(individual_gcm_features, to = c(0,1)),
    individual_mgl_features = scales::rescale(individual_mgl_features, to = c(0,1)),
    post.reg.av = scales::rescale(post.reg.av, to = c(0,1))
  )

@@

t3la = t3 %>% 
  select(
    word,
    lex_typicality,
    baseline.gcm,
    baseline.mgl,
    reg.av
  ) %>% 
  rename(
    GCM = baseline.gcm,
    MGL = baseline.mgl,
    participants = reg.av
  ) %>% 
  gather(type, baseline.averages, -word, -lex_typicality)

t3lb = t3 %>% 
  select(
    word,
    lex_typicality,
    individual.gcm,
    individual.mgl,
    post.reg.av
  ) %>% 
  rename(
    GCM = individual.gcm,
    MGL = individual.mgl,
    participants = post.reg.av
  ) %>% 
  gather(type, individual.averages, -word, -lex_typicality)

t4 = full_join(t3la,t3lb, by = c("word", "lex_typicality", "type"))

@@

ggplot(t4, aes(x = baseline.averages, y = individual.averages, colour = lex_typicality, shape = lex_typicality)) +
  guides(size = F) +
  geom_point() +
  geom_smooth(se = F, method = 'loess', formula = 'y ~ x') +
  facet_wrap( ~ type)
ggsave('interactionplot.pdf', device = cairo_pdf, width = 12.5, height = 4)

>>>>

try(setwd('../../models/paper'))
try(setwd('~/Github/RaczBecknerHayPierrehumbert2019/models/paper'))
```

@@

```{r }
source('../../functions/grabdata.R')

@@

save(fit1, file = '../../models/paper/bayes_fit1.rda')

@@

save(fit2, file = '../../models/paper/bayes_fit2.rda')

@@

save(fit3, file = '../../models/paper/bayes_fit3.rda')

@@

save(fit4, file = '../../models/paper/bayes_fit4.rda')

@@

loo.comparisons = loo_compare(fit1,fit2,fit3,fit4)
save(loo.comparisons, file = '../../models/paper/loo_comparisons.rda')

@@

load('../../models/paper/bayes_fit3.rda')
bayes_factor()

load('../../models/paper/loo_comparisons.rda')
loo.comparisons

@@

save(m3, file = '../../models/paper/m3.rda')

@@

save(m4, file = '../../models/paper/m4.rda')
```

@@

load('../../models/paper/m4.rda')
load('../../models/paper/m3.rda')

@@

m5 <- glmer(resp_post_reg ~ c.baseline_gcm_features + gcm_wf_score_diff + pre_reg_av + (1 + c.baseline_gcm_features + gcm_wf_score_diff | participant_id) + (1 | word), data = test2, family = binomial (link = logit), control=glmerControl(optimizer="bobyqa"))
save(m5, file = '../../models/paper/m5.rda')

m6 <- glmer(resp_post_reg ~ c.baseline_mgl_features + mgl_wf_score_diff + pre_reg_av + (1 + c.baseline_mgl_features + mgl_wf_score_diff | participant_id) + (1 | word), data = test2, family = binomial (link = logit), control=glmerControl(optimizer="bobyqa"))
save(m6, file = '../../models/paper/m6.rda')

@@

m7 <- glmer(resp_post_reg ~ c.individual_gcm_features + c.baseline_mgl_features + pre_reg_av + (1 + c.individual_gcm_features + c.baseline_mgl_features | participant_id) + (1 | word), data = test2, family = binomial (link = logit), control=glmerControl(optimizer="bobyqa"))
save(m7, file = '../../models/paper/m7.rda')

@@

```{r }
load('../../models/paper/m5.rda')
load('../../models/paper/m6.rda')
load('../../models/paper/m7.rda')

@@

t2 = test2 %>%
  mutate(lex_typicality2 = 
           case_when(
             lex_typicality == 'atypical' ~ 'reversed',
             lex_typicality == 'typical' ~ 'typical',
             lex_typicality == 'random' ~ 'random',
           ),
         lex_typicality2 = factor(lex_typicality2, levels = c('typical', 'reversed', 'random'))
         ) %>% 
  group_by(
    word, 
    lex_typicality2
  ) %>% 
  summarise(
    post.reg.av = mean(resp_post_reg),
    individual_gcm_features = mean(individual_gcm_features),
    individual_mgl_features = mean(individual_mgl_features),
  ) %>% 
  ungroup() %>% 
  mutate(
    individual_gcm_features = scales::rescale(individual_gcm_features, to = c(0,1)),
    individual_mgl_features = scales::rescale(individual_mgl_features, to = c(0,1)),
    post.reg.av = scales::rescale(post.reg.av, to = c(0,1))
  )

@@

t3la = t3 %>% 
  select(
    word,
    lex_typicality2,
    baseline.gcm,
    baseline.mgl,
    reg.av
  ) %>% 
  rename(
    GCM = baseline.gcm,
    MGL = baseline.mgl,
    participants = reg.av
  ) %>% 
  gather(type, baseline.averages, -word, -lex_typicality2)

t3lb = t3 %>% 
  select(
    word,
    lex_typicality2,
    individual.gcm,
    individual.mgl,
    post.reg.av
  ) %>% 
  rename(
    GCM = individual.gcm,
    MGL = individual.mgl,
    participants = post.reg.av
  ) %>% 
  gather(type, individual.averages, -word, -lex_typicality2)

t4 = full_join(t3la,t3lb, by = c("word", "lex_typicality2", "type"))

@@

ggplot(t4, aes(x = baseline.averages, y = individual.averages, colour = lex_typicality2, shape = lex_typicality2)) +
  guides(size = F) +
  geom_point() +
  geom_smooth(se = F, method = 'loess', formula = 'y ~ x') +
  facet_wrap( ~ type) +
  scale_shape_discrete(name="Lexical\ntypicality") +
  scale_colour_discrete(name="Lexical\ntypicality") +
  xlab('verb baseline average') +
  ylab('verb ESP average')
# ggsave('interactionplot.pdf', device = cairo_pdf, width = 12.5, height = 4)
ggsave('fig4_2019.pdf', width = 12.5, height = 4)
